Using Scipion for Stream Image Processing at EM Facilities

### 2018-03-29 scipionbox-abstract-only.tex
Added abstract only file for ACA conference

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}
\author{Scipion Boys$^{(a)}$,\\
Jos\'e Miguel de la Rosa-Trev\'{i}n$^{(c)}$,\\
Marta Carroni$^{(c)}$,\\
Stefan Fleichman$^{(c)}$,\\
Erik Lindahl$^{(c,d)}$\\
Ashton AW$^{(e)}$,\\
Basham M$^{(e)}$,\\
Clare DK$^{(e)}$,\\
Savage K$^{(e)}$,\\
Siebert CA$^{(e)}$,\\
        }

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(c)}$ Department of Biochemistry and Biophysics, Science for Life Laboratory, Stockholm University, Stockholm, Sweden}} 
\lyxaddress{{\small$^{(d)}$ Swedish e-Science Research Center, KTH Royal Institute of Technology, Stockholm, Sweden}}
\lyxaddress{{\small$^{(e)}$ Diamond Light Source, Harwell Science and Innovation Campus, Didcot OX11 0DE, England}}
%This document provides a preliminary analysis of the data collected by the CTF Challenge (http://i2pc.cnb.csic.es/3dembenchmark/LoadHome.htm). Figures/tables/plots/etc are located at the document's end. 
\setcounter{figure}{2}%I do not know why but figure counter starts with -1
\textbf{Corresponding Author:} %Roberto Marabini, Ph= 34 91 5854510, email: roberto@cnb.csic.es\\
%Escuela Polit\'{e}cnica Superior\\
%Universidad Aut\'{o}noma de Madrid\\
%28049 Cantoblanco\\
%Madrid\\
%Spain

\newpage
\input{0.abstract.tex}
\input{1.introduction.tex}
\input{2.overall.tex}
\input{3.workflow.tex}
\input{4.results.tex}
\input{5.conclusions.tex}
\input{6.acknowledgments.tex}
\appendix

\bibliographystyle{elsart-harv}
\bibliography{large}

\clearpage
%\input{listOfFigures.tex}

\newpage
%tables
%\input{numberImagesDataSet.tex}
%%%%%\input{markersLegend.tex}
%\input{numberImagesUpload.tex}
%\newpage

>>>>

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}

\author{
J.M. de la Rosa-Trev\'{i}n$^{(c)}$, \\
J. G\'omez-Blanco$^{(b)}$, P. Conesa, Y. Rancel, L. del Cano, \\
R. Arranz, F.J. Chich\'on, J. Mart\'in-Benito, \\
M. Carroni$^{(c)}$, S. Fleichman$^{(c)}$, E. Lindahl$^{(c,d)}$,\\ 
M. Basham M$^{(e)}$, D.K. Clare $^{(e)}$, K. Savage$^{(e)}$, \\
C.A. Siebert CA$^{(e)}$, A.W, Ashton$^{(e)}$, \\
R. Marabini $^{(a,b)}$, C.O.S. Sorzano$^{(b)}$, J.M. Carazo $^{(b)}$ 
}

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(c)}$ Department of Biochemistry and Biophysics, Science for Life Laboratory, Stockholm University, Stockholm, Sweden}} 
\lyxaddress{{\small$^{(d)}$ Swedish e-Science Research Center, KTH Royal Institute of Technology, Stockholm, Sweden}}
\lyxaddress{{\small$^{(e)}$ Diamond Light Source, Harwell Science and Innovation Campus, Didcot OX11 0DE, England}}

\newpage
\input{0.abstract.tex}
